
% Thesis statement of originality -------------------------------------

% Depending on the regulations of your faculty you may need a declaration like the one below. This specific one is from the medical faculty of the university of Dresden.

\chapter {Publication List}       %this creates the heading for the declaration page
\label{chap:PubList}

%------------------------------------------------------------------------------------
\section*{Journal Papers}
%------------------------------------------------------------------------------------
\begin{enumerate}

\item Ryo Aihara, Ryoichi Takashima, Tetsuya Takiguchi and Yasuo Ariki:
``Noise-Robust Voice Conversion Based on Sparse Spectral Mapping Using Non-negative Matrix Factorization'',
\textit{IEICE Transactions on Information and Systems}, Vol.E97-D, No.6, pp.1411-1418, 2014.

\item Yuki Takashima, Yasuhiro Kakihara, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki, Nobuyuki Mitani, Kiyohiro Omori, Kaoru Nakazono:
``Audio-Visual Speech Recognition Using Convolutive Bottleneck Networks for a Person with Severe Hearing Loss'',
\textit{IPSJ Transactions on Computer Vision and Applications}, Vol. 7, pp. 64-68, 2015.

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Individuality-Preserving Voice Conversion for Articulation Disorders Using Phoneme-Categorized Exemplars'',
\textit{ACM Transactions on Accessible Computing (TACCESS)}, Vol. 6, No. 4, pp. 13:1-13:17, 2015.

\item Masaka Kenta, Aihara Ryo, Takiguchi Tetsuya, Ariki Yasuo:
``Multimodal voice conversion based on non-negative matrix factorization'',
\textit{EURASIP Journal on Audio, Speech, and Music Processing}, 2015:24 DOI: 10.1186/s13636-015-0067-4m 2015.

\item Ryo Aihara, Takao Fujii, Toru Nakashika, Tetsuya Takiguchi, Yasuo Ariki:
``Small-parallel exemplar-based voice conversion in noisy environments using affine non-negative matrix factorization'',
\textit{EURASIP Journal on Audio, Speech, and Music Processing}, 2015:32 doi:10.1186/s13636-015-0075-4, 2015.

\item Ryo Aihara, Testuya Takiguchi, Yasuo Ariki:
``Multiple Non-negative Matrix Factorization for Many-to-many Voice Conversion'',
\textit{IEEE/ACM Transactions on Audio, Speech, and Language Processing}, Vol. 24, No. 7, pp. 1175-1184 2016.

\end{enumerate}

%------------------------------------------------------------------------------------
\section*{International Conference Papers}
%------------------------------------------------------------------------------------
\begin{enumerate}

\item  Ryo AIHARA, Toru NAKASHIKA, Tetsuya TAKIGUCHI, Yasuo ARIKI:
``VOICE CONVERSION BASED ON NON-NEGATIVE MATRIX FACTORIZATION USING PHONEME-CATEGORIZED DICTIONARY'',
\textit{ICASSP 2014}, pp.7944-7948, 2014.

\item  Kenta MASAKA, Ryo AIHARA, Tetsuya TAKIGUCHI, Yasuo ARIKI:
``MULTIMODAL VOICE CONVERSION USING NON-NEGATIVE MATRIX FACTORIZATION IN NOISY ENVIRONMENTS'',
\textit{ICASSP 2014} , pp.1561-1565, 2014.

\item  Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Individuality-preserving Voice Conversion for Articulation Disorders Using Dictionary Selective Non-negative Matrix Factorization'',
\textit{SLPAT 2014, 5th Workshop on Speech and Language Processing for Assistive Technologies}, pp. 29-37, 2014.

\item  E. Byambakhishig, K. Tanaka, R. Aihara, T. Nakashika, T. Takiguchi, Y. Ariki:
``Error Correction of Automatic Speech Recognition Based on Normalized Web Distance'',
\textit{Interspeech 2014}, pp.2852-2856, 2014.

\item  Kenta Masaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Multimodal Exemplar-based Voice Conversion using Lip Features in Noisy Environments'',
\textit{Interspeech 2014}, pp.1159-1163, 2014.

\item Ryo AIHARA, Reina UEDA, Tetsuya TAKIGUCHI, Yasuo ARIKI:
``Exemplar-based Emotional Voice Conversion Using Non-negative Matrix Factorization'',
\textit{APSIPA 2014}, 4 pages, 2014.

\item  Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``ACTIVITY-MAPPING NON-NEGATIVE MATRIX FACTORIZATION FOR EXEMPLAR-BASED VOICE CONVERSION'',
\textit{ICASSP 2015}, pp. 4899-4903, 2015.

\item  Ryo Aihara, Takao Fujii, Tetsuya Takiguchi, and Yasuo Ariki:
``NOISE-ROBUST VOICE CONVERSION USING A SMALL PARALLEL DATA BASED ON NON-NEGATIVE MATRIX FACTORIZATION'',
\textit{The 23rd European Signal Processing Conference (EUSIPCO)}, pp.315-319, 2015.

\item  Ryo Aihara, Testuya Takiguchi, and Yasuo Ariki:
``Many-to-many Voice Conversion Based on Multiple Non-negative Matrix Factorization'',
\textit{INTERSPEECH 2015}, pp. 2749-2753, 2015.

\item  Ryo AIHARA, Kenta MASAKA, Tetsuya TAKIGUCHI, Yasuo ARIKI:
``LIP-TO-SPEECH SYNTHESIS USING LOCALITY-CONSTRAINT NON-NEGATIVE MATRIX FACTORIZATION'',
\textit{The First International Workshop on Machine Learning in Spoken Language Processing (MLSLP2015)}, 6 pages, 2015.

\item  Reina Ueda, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki :
``Individuality-Preserving Spectrum Modification for Articulation Disorders Using Phone Selective Synthesis''',
\textit{SLPAT 2015, 6th Workshop on Speech and Language Processing for Assistive Technologies}, 6 pages, 2015.

\item  Ryo Aihara, Testuya Takiguchi, and Yasuo Ariki:
``MANY-TO-ONE VOICE CONVERSION USING EXEMPLAR-BASED SPARSE REPRESENTATION'',
\textit{2015 IEEE Workshop on Applications of Signal Processing to Audio and Acoustics (WASPAA)}, 2015.

\item Ryo AIHARA, Testuya TAKIGUCHI, Yasuo ARIKI:
``SEMI-NON-NEGATIVE MATRIX FACTORIZATION USING ALTERNATING DIRECTION METHOD OF MULTIPLIERS FOR VOICE CONVERSION'',
\textit{ICASSP 2016}, pp. 5170-5174, 2016.

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for Voice Conversion Using Discriminative Graph-embedded Non-negative Matrix Factorization'',
\textit{Interspeech 2016}, pp. 292-296, 2016.

\item Yuki Takashima, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki, Nobuyuki Mitani, Kiyohiro Omori, Kaoru Nakazono:
``Audio-Visual Speech Recognition Using Bimodal-Trained Bottleneck Features for a Person with Severe Hearing Loss''',
\textit{Interspeech 2016}, pp.227-281, 2016.

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Dysarthric Speech Modification Using Parallel Utterance Based on Non-negative Temporal Decomposition'',
\textit{SLPAT 2016, 7th Workshop on Speech and Language Processing for Assistive Technologies}, pp. 75-79, 2016.

\end{enumerate}


%------------------------------------------------------------------------------------
\section*{Book}
%------------------------------------------------------------------------------------
\begin{enumerate}

\item Ryo Aihara, Kenta Masaka, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for Multimodal Voice Conversion Using Matrix Factorization'',
\textit{Computer and Information Science}, edited by Roger Lee, Springer International Publishing, pp. 27-40, 2016.

\end{enumerate}

%------------------------------------------------------------------------------------
\section*{Technical Reports}
%------------------------------------------------------------------------------------
\begin{enumerate}

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Individuality-preserving Voice Conversion for Articulation Disorders Using Sparse Dictionary Learning'',
\textit{IEICE Technical Report}, vol. 114, no. 91, SP2014-53，pp. 39-44，2014. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Many-to-one Voice Conversion using Multiple Non-negative Matrix Factorization'',
\textit{IEICE Technical Report}, vol. 114, no. 365, SP2014-126, pp. 75-80, 2014. (in Japanese)

\item Kenta Masaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Multimodal Voice Conversion using Weighted Features in Noisy Environments'',
\textit{IEICE Technical Report}, vol. 114, no. 365, SP2014-126, pp. 87-92, 2014. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Exemplar-based Voice Conversion for Arbitrary Speakers'',
\textit{IEICE Technical Report}, vol. 115, no. 253, pp. 1-6, 2015. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for Voice Conversion Using Alternating Direction of Multipliers'',
\textit{IEICE Technical Report}, vol. 115, no. 346, SP2015-72, pp. 13-18, 2015. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for Voice Conversion Using Discriminative Graph-embedded Non-negative Matrix Factorization'',
\textit{IEICE Technical Report}, vol. 116, no. 189, SP2016-38, pp. 59-64, 2016. (in Japanese)

\end{enumerate}

%------------------------------------------------------------------------------------
\section*{Domestic Conference Papers}
%------------------------------------------------------------------------------------
\begin{enumerate}
\item Byambakhishig Enkhbolor, Katsuyuki Tanaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Error correction of automatic speech recognition based on Normalized Web Distance'',
\textit{The 28th Annual Conference of the Japanese Society for Artificial Intelligence}, 301-1in, 2014. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Exemplar-based Voice Conversion Based on Activity-adaptive Non-negative Matrix Factorization'',
\textit{Acoustical Society of Japan 2014 Autumn Meeting}, 1-7-16, pp.223-226, 2014. (in Japanese)

\item Takao Fujii, Ryo Aihara, Toru Nakashika, Tetsuya Takiguchi, Yasuo Ariki:
``Voice Conversion based on NMF using Speaker Adaptation in Noisy Environments'',
\textit{Acoustical Society of Japan 2014 Autumn Meeting}, 2-Q-36, pp. 345-348, 2014. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Many-to-one Voice Conversion Based on Multiple Non-negative Matrix Factorization'',
\textit{Acoustical Society of Japan 2015 Spring Meeting}, 3-2-2, pp. 275-278, 2015. (in Japanese)

\item Takao Fujii, Ryo Aihara, Toru Nakashika, Tetsuya Takiguchi, Yasuo Ariki:
``Voice Conversion using a Small Parallel Corpus based on Non-negative Matrix Factorization in Noisy Environments'',
\textit{Acoustical Society of Japan 2015 Spring Meeting}, 2-Q-39, pp. 393-396, 2015. (in Japanese)

\item Kenta Masaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Speech Production from Lip Images based on Non-negative Matrix Factorization'',
\textit{Acoustical Society of Japan 2015 Spring Meeting}, 2-Q-38, pp. 389-392, 2015. (in Japanese)

\item Yuki Takashima, Yasuhiro Kakihara, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki, Nobuyuki Mitani, Kiyohiro Omori, Kaoru Nakazono:
``Audio-Visual Speech Recognition Using Convolutive Bottleneck Networks for a Person with Severe Hearing Loss'',
\textit{MIRU 2015}, OS3-2, 2015.  (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Many-to-many Voice Conversion Based on Multiple Non-negative Matrix Factorizations'',
\textit{Acoustical Society of Japan 2015 Autumn Meeting}, pp. 227-230, 2015. (in Japanese)

\item Kenta Masaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Speech Generation from Lip Images based on Non-negative Matrix Factorization with Beta-divergence'',
\textit{Acoustical Society of Japan 2015 Autumn Meeting}, 1-Q-32, pp. 285-288, 2015. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for NMF-based Voice Conversion Using Alternating Direction Method of Multipliers'',
\textit{Acoustical Society of Japan 2016 Spring Meeting}, 1-R-36, pp.325-328, 2016. (in Japanese)

\item Kenta Masaka, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Multimodal Voice Conversion using Sparse-Parallel Training.'',
\textit{Acoustical Society of Japan 2016 Spring Meeting}, 1-R-35, pp. 321-325, 2016. (in Japanese)

\item Konjun I, Ryo Aihara, Tetsuya Takiguchi, Yasuo Ariki:
``Voice Conversion using a Small Parallel Corpus based on NMF using ADMM in Noisy Environments'',
\textit{Acoustical Society of Japan 2016 Spring Meeting}, 1-R-38, 2016. (in Japanese)

\item Ryo Aihara, Tetsuya Takiguchi, and Yasuo Ariki:
``Parallel Dictionary Learning for Voice Conversion Using Discriminative Graph-embedded Non-negative Matrix Factorization'',
\textit{Acoustical Society of Japan 2016 Autumn Meeting}, 3-5-3, pp.155-158, 2016. (in Japanese)

\end{enumerate}
\label{chap:endPubList}






% ----------------------------------------------------------------------